A fast and memory-efficient transition state search method for complex energy landscapes

### 2022-05-17 manuscript.tex
CommPhys appendicies

% Text
\usepackage{siunitx}
\usepackage{enumitem}
\usepackage{xcolor}

@@

The first system is a two-dimensional, seven-particle cluster, interacting via a Lennard-Jones pair potential.
This is a frequently used test system for studying transition rates \cite{Wales2002,Passerone2001}.
Here, the \num{14} degrees of freedom are the particle coordinates.
The characteristic transition shown in \cref{fig:speedtest}a sees a particle rearrangement between two close-packed clusters.

@@

\section{Methods}

@@

\appendix
\section*{}
\begin{acknowledgments}
  S.~J.~A. is supported by a studentship from the Engineering and Physical Sciences Research Council [Grant No. EP/R513039/1].
  H.~K. and J.~R.~P. acknowledge funding from the Engineering and Physical Sciences Research Council [Grant No. EP/V034154/1].
\end{acknowledgments}

@@

>>>>

% Text
\usepackage[group-separator={,}]{siunitx}
\usepackage{enumitem}
\usepackage{xcolor}

@@

The first system is a two-dimensional, seven-particle cluster, interacting via a Lennard-Jones pair potential.
This is a frequently used test system for studying transition rates \cite{Wales2002,Passerone2001}.
Here, the 14 degrees of freedom are the particle coordinates.
The characteristic transition shown in \cref{fig:speedtest}a sees a particle rearrangement between two close-packed clusters.

@@

\appendix
\section*{Methods}

@@

\section*{Data availability}
The data that support the findings of this study are available from the corresponding author upon reasonable request.

\section*{Code availability}
The code used in this study is available from the corresponding author upon reasonable request.

@@

\begin{acknowledgments}
  S.~J.~A. is supported by a studentship from the Engineering and Physical Sciences Research Council [Grant No. EP/R513039/1].
  H.~K. and J.~R.~P. acknowledge funding from the Engineering and Physical Sciences Research Council [Grant No. EP/V034154/1].
\end{acknowledgments}

\section*{Author contributions}
S.~J.~A. and J.~R.~P. developed the theoretical model.
S.~J.~A. performed the experiments and analysed the data.
H.~K. supervised the study.
S.~J.~A. wrote the paper, with review and input from H.~K. and J.~R.~P.

\section*{Competing interests}
The authors declare no competing interests.
